Ecological network control" <!-- DBS really doesn't like the new title... -->

### 2018-04-20 publication/manuscript.Rmd

---
title: "Ecological network control" <!-- DBS really doesn't like the new title... -->
classoption: a4paper
csl: journal-of-ecology.csl
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    number_sections: false
toc: false
header-includes:
- \usepackage{setspace}
- \usepackage{float}
- \usepackage{booktabs}
- \usepackage{caption}
- \usepackage{lineno}
documentclass: artikel1
bibliography: references.bib
---

@@

```{r example_network, include = F}
loadd(example_net)

>>>>

---
title: "Ecological network control" <!-- DBS really doesn't like the new title... -->
classoption: a4paper
csl: journal-of-ecology.csl
output: 
  bookdown::pdf_document2: 
    keep_tex: yes
    number_sections: false
toc: false
header-includes:
- \usepackage{setspace}
- \usepackage{float}
- \usepackage{booktabs}
- \usepackage{caption}
- \usepackage{lineno}
- \usepackage{xr}
- \externaldocument[S-]{supp-info}
documentclass: artikel1
bibliography: references.bib
---

@@

```{r load-metadata}
loadd(metadata)
lop <- filter(metadata, study == "lopezaraiza") %>% mutate(size = n_pla + n_pol) %$% size %>% summary() 
bar <- filter(metadata, study == "bartomeus") %>% mutate(size = n_pla + n_pol) %$% size %>% summary() 
```

We apply methods of control theory to ten paired pollination networks.
Each network pair was composed of a community invaded by a plant and a community free of the invasive species. 
Four pairs were obtained from natural or semi-natural vegetation communities in the city of Bristol, UK [@Lopezaraiza-Mikel2007]. 
These networks are comprised of `r lop[1]`--`r lop[6]` species (mean `r round(lop[4])`), and non-invaded plots were obtained by experimentally removing all the flowers of the invasive species *Impatients grandulifera*.
The other six pairs were obtained from lower diversity Mediterranean shrublands in Cap de Creus National Park, Spain [@Bartomeus2008].
These networks are comprised of `r bar[1]`--`r bar[6]` species (mean `r round(bar[4])`); in contrast to the above, uninvaded communities were obtained from plots that had not yet been colonised by either of the invasive species *Carpobrotus affine acinaciformis* or *Opuntia stricta*.  
Supplementary Information S\@ref(S-empirical-networks)

```{r example-network, include = F, eval = F}
loadd(example_net)
